word lists

### 2022-03-30 analysis/word_lists.Rmd
prep model run on cluster

write_xlsx(md, path = "../data/word_list.xlsx")
```

@@

write_csv(fw, file = "../data/word_list.csv")

@@

>>>>

#write_xlsx(md, path = "../data/word_list.xlsx")
```

@@

## add words from clt round 2 selection

fl <- fw%>%
  bind_rows(read_xlsx("../data/annotated_word_lists/clt_new_words_round2.xlsx")%>%mutate(word_type = "noun")%>%filter(select == "x"))

#write_csv(fl, file = "../data/word_list.csv")

@@

# CLT comprehension items

## Generate list to be selected from

```{r}
sclt <- read_csv(file = "../data/word_list.csv")%>%
  left_join(setal%>%select(german, sem_cat, familiarity_m, typicality_m, -sem_cat))%>%
  select(-select, -aoa_mor, -english, -clt)%>%
  filter(word_type == "noun",
         aoa_german_comb > 5.94)%>%
  mutate(select = NA,
         sem_dom = NA)%>%
  select(-word_type)

#write_xlsx(sclt, path = "../data/clt_new_words.xlsx")
```

## Generate List for second round of selection

```{r}
# words selected for CLT from previously selected words
clt_sel1 <- read_xlsx("../data/annotated_word_lists/clt_new_words.xlsx")

# full list for questionnaire

file.list <- list.files(path = "../data/annotated_word_lists/", pattern='*.xlsx', full.names = T)

qd <- lapply(file.list, read_xlsx)%>%bind_rows()%>%
  arrange(aoa_german_comb)%>%
  select(1:9, -aoa_mor, - familiarity_m, -typicality_m)%>%
  left_join(setal%>%select(german, familiarity_m, typicality_m, -sem_cat))%>%
  filter(aoa_german_comb > 5.94)%>%
  select(-select, - clt)%>%
  mutate(familiarity_m = round(familiarity_m, 2), 
         typicality_m = round(typicality_m, 2))

sclt2 <- qd %>% left_join(clt_sel1)

#write_xlsx(sclt2, path = "../data/clt_new_words_round2.xlsx")

## selected words round 2

```{r}
# words selected for CLT from previously selected words
clt_sel <- read_xlsx("../data/annotated_word_lists/clt_new_words_round2.xlsx")%>%
  filter(select == "x")%>%
  group_by(sem_dom)

#write_xlsx(clt_sel, path = "../data/clt_new_words.xlsx")
```
